On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-06 arity1pyramid.tex
Intro modified
fix pyramid pic
Add files via upload

\subsection{$\alpha = 1$, arbitrary alphabets}
First we present a lower bound construction for arity $1$ systems. At $\alpha=1$, having delay $\delta=2$ allows the deterministic folding of quadratic length transcripts compared with $\delta=1$, where, as stated before, the maximum length is linear in the length of the seed. We demonstrate this with an infinite family of OS, which fold deterministically a transcript of length $\frac{(n-1)^2}{4}$ starting from a given seed of length $n$.

Consider the following $\delta=2$, $\alpha=1$ system with bead types $\{0,1,2,3,4\}$ and attraction rules $\{(1,1),(2,2), (3,3),(4,4)\}$. Let the seed $\sigma$ be a conformation of a $4k+1$ long bead sequence of the form $(1020)^k0$, such that bead $\sigma[i]$ of the seed is stabilized at point $(i,0)$, for all $1\leq i\leq 4k-1$. Bead $4k$ is at $(4k-1,-1)$ and bead $4k+1$ is at $(4k,0)$.
\vspace{0.1cm}

The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where $\mathrm{row}_\ell$, for $\ell\in \{1,\dots, 2k\}$ is given in the table of Fig.~\ref{table:transcript}.
\begin{figure}[h]
	\begin{minipage}{.49\textwidth}
		%\centering
		\begin{tabular}{l|l}
			\multicolumn{2}{c}{Transcript $w$}\\
			\multicolumn{2}{c}{}  \\
			$k$ odd & \hspace{0.3cm} $k$ even\\\hline
			& \\
			$(2413)^{k-1}241$\hspace{0.3cm} & \hspace{0.3cm} $(2413)^{k-1}241$\\
			$(4231)^{k-1}4$   &  \hspace{0.3cm} $(4231)^{k-1}4$  \\
			$(1324)^{k-2}132$ &  \hspace{0.3cm} $(1324)^{k-2}132$\\
			$(3142)^{k-2}3$   &  \hspace{0.3cm} $(3142)^{k-2}3$ \\
			\vdots			 &  \hspace{0.3cm} \vdots\\
			$(1324)^1 132$	 &  \hspace{0.3cm} $(2413)^{1} 241$\\
			$(3142)^1 3$		 & \hspace{0.3cm} $(4231)^1 4$\\
			$(2413)^0 241$	 &  \hspace{0.3cm} $(1324)^0 132$\\
			$(4231)^0 4$		 & \hspace{0.3cm} $(3142)^0 3$\\
		\end{tabular}
	\end{minipage}
	%\scriptsize
	\begin{minipage}{.49\textwidth}
		%\centering
		\begin{tabular}{|l|c|}
			\hline
			\hspace{1.2cm}row $\ell$ & $\ell\mod 4$ \\\hline
			 & \\
			\hspace{0.1cm}$(2413)^{k-\lfloor (\ell+1)/2\rfloor}241$ \hspace{0.1cm} &  $\textrm{ }\ell\equiv 1\mod 4\textrm{ }$\\
			\hspace{0.1cm}$(4231)^{k-\lfloor (\ell+1)/2\rfloor}4$   &  $\textrm{ }\ell\equiv 2 \mod 4\textrm{ }$ \\
			\hspace{0.1cm}$(1324)^{k-\lfloor (\ell+1)/2\rfloor}132$ &  $\textrm{ }\ell\equiv 3 \mod 4\textrm{ }$ \\
			\hspace{0.1cm}$(3142)^{k-\lfloor (\ell+1)/2\rfloor}3$   &  $\textrm{ }\ell\equiv 4 \mod 4\textrm{ }$ \\\hline
		\end{tabular}

	\end{minipage}
	\caption{Transcript of pyramid-like conformation at delay $2$, arity $1$.}
	\label{table:transcript}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{./Fig/CI_Numbers}
	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. }
	\label{CI:big}
\end{figure}

>>>>

%\subsection{$\alpha = 1$, arbitrary alphabets}
First we present a lower bound construction for arity $1$ systems. At $\alpha=1$, having delay $\delta=2$ allows the deterministic folding of quadratic length transcripts compared with $\delta=1$, where, as stated before, the maximum length is linear in the length of the seed. We demonstrate this with an infinite family of OS, which fold deterministically a transcript of length $\frac{(n-1)^2}{4}$ starting from a given seed of length $n$.

Consider the following $\delta=2$, $\alpha=1$ system with bead types $\{0,1,\dots,8\}$ and attraction rules $\{(i,i) \mid 1\leq i\leq 8\}$. Let the seed $\sigma$ be a conformation of a $4k+1$ long bead sequence of the form $(10205060)^{k/2}0$ and $(10205060)^{(k-1)/2}(1020)0$, for $k$ even and odd, respectively. Bead $\sigma[i]$ of the seed is stabilized at point $(i,0)$, for all $1\leq i\leq 4k-1$. Bead $4k$ is at $(4k-1,-1)$ and bead $4k+1$ is at $(4k,0)$.
\vspace{0.1cm}

The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where 
\begin{itemize}
	\item $\mathrm{row}_1=(24136857)^{(k-1)/2}241$ if $k$ is odd, and $\mathrm{row}_1=(68572413)^{k/2-1}6857241$ if $k$ is even;
	\item $\mathrm{row}_{i+1}=(\mathrm{row}_i[2..|\mathrm{row}_i|-1])^r$ for $i\in \{1,\dots, 2k-1\}$, that is each row is the reverse of the previous without the first and last bead.
\end{itemize}

%The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where $\mathrm{row}_\ell$, for $\ell\in \{1,\dots, 2k\}$ is given in the table of Fig.~\ref{table:transcript}.
%\begin{figure}[h]
%%	\begin{minipage}{.49\textwidth}
%%		%\centering
%%		\begin{tabular}{l|l}
%%			\multicolumn{2}{c}{Transcript $w$}\\
%%			\multicolumn{2}{c}{}  \\
%%			$k$ odd & \hspace{0.3cm} $k$ even\\\hline
%%			& \\
%%			$(24136857)^{(k-1)/2}241$\hspace{0.3cm} & \hspace{0.3cm} $(2413)^{k-1}241$\\
%%			$42(75863142)^{k-1}314$   &  \hspace{0.3cm} $(4231)^{k-1}4$  \\
%%			$13(68572413)^{k-2}2$ &  \hspace{0.3cm} $(1324)^{k-2}132$\\
%%			$(3142)^{k-2}3$   &  \hspace{0.3cm} $(3142)^{k-2}3$ \\
%%			\vdots			 &  \hspace{0.3cm} \vdots\\
%%			$(1324)^1 132$	 &  \hspace{0.3cm} $(2413)^{1} 241$\\
%%			$(3142)^1 3$		 & \hspace{0.3cm} $(4231)^1 4$\\
%%			$(2413)^0 241$	 &  \hspace{0.3cm} $(1324)^0 132$\\
%%			$(4231)^0 4$		 & \hspace{0.3cm} $(3142)^0 3$\\
%%		\end{tabular}
%%	\end{minipage}
%	%\scriptsize
%	\begin{minipage}{.99\textwidth}
%		\centering
%		\begin{tabular}{|l|c|}
%			\hline
%			\hspace{1.2cm}row $\ell$ & $\ell\mod 4$ \\\hline
%			 & \\
%			\hspace{0.1cm}$(24136857)^{k-\lfloor (\ell+1)/2\rfloor}241$ \hspace{0.1cm} &  $\textrm{ }\ell\equiv 1\mod 4\textrm{ }$\\
%			\hspace{0.1cm}$(4231)^{k-\lfloor (\ell+1)/2\rfloor}4$   &  $\textrm{ }\ell\equiv 2 \mod 4\textrm{ }$ \\
%			\hspace{0.1cm}$(1324)^{k-\lfloor (\ell+1)/2\rfloor}132$ &  $\textrm{ }\ell\equiv 3 \mod 4\textrm{ }$ \\
%			\hspace{0.1cm}$(3142)^{k-\lfloor (\ell+1)/2\rfloor}3$   &  $\textrm{ }\ell\equiv 4 \mod 4\textrm{ }$ \\\hline
%		\end{tabular}
%	
%	\end{minipage}
%	\caption{Transcript of pyramid-like conformation at delay $2$, arity $1$.}
%	\label{table:transcript}
%\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{./Fig/CI_NumbersNew}
	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. }
	\label{CI:big}
\end{figure}
